---
title: "Exploratory Analysis"
output: html_document
---

## Project title

Give your project a concise, interesting title that summarizes the entirety of your project

### Authors

Names of your team members

### Date

Winter 2022

### Abstract

No more than three sentences that summarize your project. Focus on the very most important aspects. For example: (1) "Our main question is .... This question is important because .... To address the question, we will ...." (2) "We are concerned with ..., because .... To address this concern, we plan to ...." (3) "Consider that .... This is important because .... Accordingly, we plan to ...."

### Keywords

3-5 keywords that summarize your project.
(e.g., "Keywords: human physiology; bicycle exercise; Gen Z; times-series data")

### Introduction  

Briefly introduce your project.  Include 3-5 research questions. What motivates the questions? Why are they important? (at least 200 words)

### Related Work  

Describe your topic and related work in this space. You must include 3 citations to related work (URLs to similar work, high quality articles from the popular press, research papers, etc. ) Please use a standard citation style of your choice. (at least 200 words)

### The Dataset

Where did you find the data? Please include a link to the data source  
Who collected the data?  
How was the data collected or generated?  
Why was the data collected?  
How many observations (rows) are in your data?  
How many features (columns) are in the data?  
What, if any, ethical questions or questions of power do you need to consider when working with this data?  
What are possible limitations or problems with this data?   (at least 200 words)

### Implications

Assuming you answer your research questions, briefly describe the expected or possible implications for technologists, designers, and policymakers. (at least 150 words)

### Limitations & Challenges
What challenges or limitations might you need to address with your project idea more broadly? Briefly discuss. (at least 150 words)

### Summary Information

Write a summary paragraph of findings that includes the 5 values calculated from your summary information R script

### Table

Include a table of aggregate information

Describe why you included the table and what information it reveals

### Chart 1

Selecting the appropriate type of chart or graph is vital when visualizing data. It guarantees that the information is presented in a clear and understandable format, especially when dealing with categorical values like the different genres of the top 1000 highest-grossing movies. A bar chart is often the most effective choice in this case as it provides a simple way to comprehend the data. The chart reveals that some movies belong to more than one genre, making it difficult to determine the most prevalent genre. Nevertheless, the chart highlights the genre that appears frequently in the top 1000 highest-earning movies, considering the revenue generated globally by each genre. This enables us to identify the frequently occurring genre while providing a comprehensive overview of the data. 

```{r, echo = FALSE, code = readLines("chart1_example.R")}
print(bar_chart)
```

### Chart 2

Include a chart

Describe why you chose this chart and what information it reveals

### Chart 3

Include a chart
``````{r, echo = FALSE, code = readLines("Chart3.R")}
```

Describe why you chose this chart and what information it reveals
